Title

### 2013-03-18 inc/hardware/column.tex
added aligner picture
added additional pictures to the hardware section

>>>>

  \begin{figure}
    \centering
    \includegraphics{chamber.jpg}
    \caption[Side view of main chamber]{
      Assembled side view of the main chamber section of the UEM column at UIC.
      To the left are the high-voltage passthrough and ``port aligner'' to which the cathode is mounted.
      Visible inside the window are the cathode Wehnelt and photocathode (left), the side of the anode, and the side of the deflector plates assembly just after the anode (right).
      The anode and plate-assembly are mounted by the ``eV parts'' system attached to the main chamber.
      The wires and connectors supplying the voltage to the plates are also clearly visible.
    }
    \label{fig:chamber-pic}
  \end{figure}

### 2013-03-18 inc/hardware/deflector.tex
work on short titles for figures (continuing)
added additional pictures to the hardware section

\begin{figure}
  \centering
  \include{deflector_schematic}
  \caption{
    Schematic diagram of one pair of deflection plates.
    The blue ray represents the path of the pulse as a whole (not to be confused with the plot of a lens).
  }
  \label{fig:deflector_schematic}
\end{figure}

@@

>>>>

\begin{figure}
  \centering
  \include{deflector_schematic}
  \caption[Schematic diagram of one pair of deflection plates]{
    Schematic diagram of one pair of deflection plates.
    The blue ray represents the path of the pulse as a whole (not to be confused with the plot of a lens).
  }
  \label{fig:deflector_schematic}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{deflector_plates.jpg}
  \caption[Picture of custom deflector plates]{
    Picture of the custom built deflector plates for use in the UEM at UIC.
    A pair of vertical and horizontal plates are mounted in a non-conductive housing.
    Each plate has a pin for connecting to voltage or ground.
    Clearance drilled holes allow mounting onto the ``eV parts'' cage inside the chamber.
  }
  \label{fig:deflector-plates-pic}
\end{figure}
